---
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
  word_document: default
bibliography: library.bib
csl: methods-in-ecology-and-evolution.csl
urlcolor: black
linkcolor: black
fontsize: 12pt
geometry: inner=1.7cm,outer=2.7cm,top=2cm,bottom=2cm,bindingoffset=1.2cm
papersize: a4paper
header-includes:
- \usepackage{placeins}
- \usepackage{fancyhdr}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \usepackage{microtype}
- \onehalfspacing
- \counterwithin{figure}{section}
- \counterwithin{table}{section}
- \usepackage{graphicx}
- \usepackage{pdflscape}
- \usepackage{enumitem}
---

---
nocite: | 
  @Example1999, @Example2000
...

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path = 'gambar/',fig.align = 'center',fig.width = 7,fig.height = 4,
                      echo = FALSE, warning = FALSE, message = FALSE)
```

\pagenumbering{gobble}

```{r child = 'Cover.Rmd'}
```

\newpage

```{r child = 'Pernyataan.Rmd'}
```


\newpage
\pagestyle{fancy}

\fancyhead[LE,RO]{}
\fancyhead[LO,RE]{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\pagenumbering{roman}

\fancyhead[CO,CE]{\scriptsize Abstract}
\fancyfoot{}
\fancyfoot[L]{\scriptsize Perencanaan Drainase Kecamatan Purwakarta}
\fancyfoot[RO,LE]{\scriptsize \thepage}
\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}

```{r child = 'abstract.Rmd'}
```

\newpage
\fancyhead[CO,CE]{\scriptsize Kata Pengantar}
\section*{Kata Pengantar}
\addcontentsline{toc}{section}{Kata Pengantar}

```{r child = 'Kata_Pengantar.Rmd'}
```

\newpage
\fancyhead[CO,CE]{\scriptsize Daftar Isi}
\setcounter{tocdepth}{2}
\addcontentsline{toc}{section}{Daftar Isi}
\renewcommand{\contentsname}{Daftar Isi}
\tableofcontents


\renewcommand{\tablename}{Tabel}
\renewcommand{\figurename}{Gambar}

\newpage
\fancyhead[CO,CE]{\scriptsize Daftar Gambar}
\addcontentsline{toc}{section}{Daftar Gambar}
\renewcommand{\listfigurename}{Daftar Gambar}
\listoffigures


\newpage
\fancyhead[CO,CE]{\scriptsize Daftar Tabel}
\addcontentsline{toc}{section}{Daftar Tabel}
\renewcommand{\listtablename}{Daftar Tabel}
\listoftables

\newpage
\pagenumbering{arabic}

\newpage
\fancyhead[CO,CE]{\scriptsize Pendahuluan}

```{r child = 'Bab_1.Rmd'}
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{\scriptsize Gambaran Umum}

```{r child = 'Bab_2.Rmd'}
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{\scriptsize Analisa Hidrologi}

```{r child = 'Bab_3.Rmd'}
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{\scriptsize Analisa Hidrolika}

```{r child = 'Bab_4.Rmd'}
```

\newpage
\pagenumbering{roman}

\FloatBarrier
\newpage
\fancyhead[CO,CE]{\scriptsize Lampiran}

```{r child = 'Lampiran.Rmd'}
```

\FloatBarrier
\newpage
\fancyhead[CO,CE]{\scriptsize Daftar Pustaka}

# Daftar Pustaka
